Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-11-04 manuscript/manuscript.tex
Adjustment to charts to better display in Manuscript
Adjusted PDF dimensions to enable better display of charts in Manuscript. Also continued editing Manuscript.

\texttt{cross\_street\_1/2} \& \texttt{intersection\_street\_1/2}: These 
two sets of street pairs are used to help identify the 
\texttt{incident address}. We found 88\% of these pairs to be 
duplicates. This duplication raises the question of which field-pair 
should be trusted; and if they are different, how should they be treated?
It is possible that these two street pairs originated from different 
agencies that used different variable names to represent the same 
information, but no documentation exists to clarify this 
relationship. These two street-pairs are highly redundant.

\begin{table}[tbp]
    \centering
    \caption{Summary of cross\_street\_1 and intersection\_street\_1}
    \label{tab:summary1}
	    \begin{tabular}{l r r}
	        \toprule
	        \textbf{category} & \textbf{count} & \textbf{percentage} \\
	        \midrule
	        Matching                    & 5,637,182 & 88.15     \\
	        Both blank -- Matching      & 1,624,499 & 25.4      \\
	        Non-matching                &   757,726 & 11.85     \\
	        cross\_street\_1\_blank     &   222,232 & N/A       \\
	        intersection\_street\_1\_blank &   519,348 & N/A       \\
	        Near-match                  &       128 & 0.002002  \\
	        \bottomrule
	    \end{tabular}
\end{table}

Table~\ref{tab:summary1} presents a summary of the matching results 
for \texttt{cross\_street\_1} and \texttt{intersection\_street\_1}. As 
the table shows, 88.15\% of the non-blank entries are exact matches.

>>>>

\texttt{cross\_street\_1/2} \& \texttt{intersection\_street\_1/2}: These 
two sets of street pairs are used to help identify the 
\texttt{incident address}. We found 88\% of these two street pairs to be 
duplicates. This duplication raises the question of which field-pair 
should be trusted; and if they are different, how should they be treated?
It is possible that these two street pairs originated from different 
agencies that used different variable names to represent the same 
information, but no documentation exists to clarify this 
relationship. These two street-pairs are highly redundant.
